A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Use Koen's abstract. It's about 20% cooler.

\begin{abstract}
Developing web applications, especially applications which need to communicate
with a server, is often a painful experience. What is conceptually a single
monolithic application is forcefully split into a client and a server
explicitly communicating over the network, with all the code duplication,
complexity and lost type safety this entails.

We propose instead a development model in which a web application is written
and compiled as a whole, allowing for synchronous, type safe client-server
communication without the need for explicit networking code, as well as the
sharing of code between client and server.
\end{abstract}

>>>>

\begin{abstract}
We propose a new programming model for web applications which is (1)
seamless; one program and one language is used to produce code for
both client and server, (2) client-centric; the programmer takes the
viewpoint of the client that runs code on the server rather than the
other way around, and (3) functional and type-safe; everything is
implemented as a Haskell library that implicitly takes care of all
networking code. Our aim is to improve the painful and error-prone
experience of today's standard development methods, in which clients
and servers are coded in different languages and communicate with each
other using ad-hoc protocols. We present the design of our library
called Haste.App, an example web application that uses it, and discuss
the implementation and the compiler technology on which it depends.
\end{abstract}
